\Sof{TBA - New Titles in the comments}

### 2020-05-04 paper/icsme20.tex
luis comments fix

From a methodological 
perspective, we leveraged a dataset of $1335$ security patches collected from open-source 
software. We calculate software maintainability before and after the patch to measure its 
impact. This empirical study presents evidence that changes 
applied in the code bases to patch vulnerabilities affect code maintainability. Especially, 
for patches that address \emph{Improper Restriction of Operations within the Bounds of 
a Memory Buffer} (CWE-119), \emph{Path Traversal} (CWE-22), \emph{Missing Release of Memory 
after Effective Lifetime} (CWE-401) and \emph{Information Exposure} (CWE-200)\Luis{Little information is known about..}.
This is important work
because there is still little information about the impact of security patches on the software
maintainability. With this study, 
we intend to highlight the need for tools to predict the impact of patches on 
maintainability~\cite{4724577}, documentation to help developers adopt security 
best practices~\cite{6311252, 7927935, MESQUIDA201519} and the importance of integrating
security-related code evolution in computer curricula.
%
%BCH compiles the ISO/IEC 25010 into a set of $10$ guidelines that are the
%base of BCH's evaluation. Two examples are the \emph{Write Simple Units of Code}
%based on the McCabe Complexity~\cite{1702388} and \emph{Keep your code base Small}
%based on the idea that smaller code bases are easier to maintain and less prone to defects~\cite{Visser:2016:OREILLY}.
%

@@

\Luis{this passive voice here sounds a bit weird (imo)}
The methodology used to measure the impact of security patches on the
maintainability of open-source software is discussed in this section.
The methodology comprises the following steps, as illustrated in
Figure~\ref{fig:met}\Luis{could you make the numbers in the figure a bit larger}:

@@

\Luis{We already made clear that we ``evaluate the impact..'' }
To evaluate the impact of security refactorings on the maintainability of
open-source software, we use a combined dataset of security vulnerabilities which is 
the outcome of mining/manually inspect $265$ GitHub projects\Luis{:mining and manually inspecting:}. \Luis{it is not clear the connection between the 267 projects and the works we mention below. There should be a sentence here clarifying and making the connection.}. Reis and Abreu 

@@

$998$ security patches. $912$ of these patches are identified with Common Weakness
Enumeration IDs (CWE) where $59.1\%$ were scraped from the National Vulnerability Dataset (NVD) and the remaining $40.9\%$ were manually classified following the \texttt{Research Concepts} view map from the CWE's list.

>>>>

From a methodological 
perspective, we leveraged a dataset of $1335$ security patches collected from open-source 
software. We calculate software maintainability before and after the patch to measure its 
impact. This empirical study presents evidence that changes 
applied in the code bases to patch vulnerabilities affect code maintainability. Especially, 
for patches that address \emph{Improper Restriction of Operations within the Bounds of 
a Memory Buffer} (CWE-119), \emph{Path Traversal} (CWE-22), \emph{Missing Release of Memory 
after Effective Lifetime} (CWE-401) and \emph{Information Exposure} (CWE-200)\Luis{Little information is known about..}\Sof{Do you want me to explain what is each vulnerability?}.
This is important work
because there is still little information about the impact of security patches on the software
maintainability. With this study, 
we intend to highlight the need for tools to predict the impact of patches on 
maintainability~\cite{4724577}, documentation to help developers adopt security 
best practices~\cite{6311252, 7927935, MESQUIDA201519} and the importance of integrating
security-related code evolution in computer curricula.
%
%BCH compiles the ISO/IEC 25010 into a set of $10$ guidelines that are the
%base of BCH's evaluation. Two examples are the \emph{Write Simple Units of Code}
%based on the McCabe Complexity~\cite{1702388} and \emph{Keep your code base Small}
%based on the idea that smaller code bases are easier to maintain and less prone to defects~\cite{Visser:2016:OREILLY}.
%

@@

In this section, we discuss the methodology used to measure
the impact of security patches on the maintainbility of open-source
software. The methodology comprises the following steps, as illustrated in
Figure~\ref{fig:met}.

@@

We use a combined dataset of security vulnerabilities which is 
the outcome of mining and manually inspect a total of $265$ GitHub projects for both
datasets. Reis and Abreu 

@@

$998$ security patches. $883$ of these patches are identified with Common Weakness
Enumeration IDs (CWE) where $62.5\%$ were scraped from the National Vulnerability Dataset (NVD) and the remaining $37.5\%$ were manually classified following the \texttt{Research Concepts} CWE's list.
